### 2019-10-15 thesis/txt/0-introduction.tex
[wip] toc corrections

\begin{itemize}
  \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
  \item[\textbf{RQ2:}] Is Programming by Example suited to extract information from CI build logs?
  \item[\textbf{RQ3:}] When are text similarity or keyword search better suited for information extraction from CI build logs?
\end{itemize}

>>>>

\begin{itemize}
  \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the extractions of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
